---
title: "ConsensusBrainEnrichRComparisons"
output: html_document
date: "2023-05-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(WGCNA)
library(readxl)
#took out samples that had Folic Acid
F_Brain <- read_excel("/Users/kchau/Documents/PEBBLES/RNA-seq_ComparisonBrain_PCBonly/F_Brain_voom_PCBonly.xlsx")
F_Brain <- F_Brain[!grepl("PLAC", colnames(F_Brain))]

M_Brain <- read_excel("/Users/kchau/Documents/PEBBLES/RNA-seq_ComparisonBrain_PCBonly/M_Brain_voom_PCBonly.xlsx")
M_Brain <- M_Brain[!grepl("PLAC", colnames(M_Brain))]

# Take a quick look at what is in the data sets (caution, longish output):
dim(F_Brain)
names(F_Brain)
dim(M_Brain)
names(M_Brain)
```


```{r}
intersectedgenes <- intersect(rownames(F_Brain), rownames(M_Brain))
F_Brain1 <- F_Brain[intersectedgenes, ]
M_Brain1 <- M_Brain[intersectedgenes, ]
```


```{r}
# We work with two sets:
nSets = 2;
# For easier labeling of plots, create a vector holding descriptive names of the two sets.
setLabels = c("Female brain", "Male brain")
shortLabels = c("Female", "Male")
# Form multi-set expression data: columns starting from 9 contain actual expression data.
multiExpr = vector(mode = "list", length = nSets)
multiExpr[[1]] = list(data = as.data.frame(t(F_Brain1[-c(1:1)])));
names(multiExpr[[1]]$data) = F_Brain1$Gene;
rownames(multiExpr[[1]]$data) = names(F_Brain1)[-c(1:1)];
multiExpr[[2]] = list(data = as.data.frame(t(M_Brain1[-c(1:1)])));
names(multiExpr[[2]]$data) = M_Brain1$Gene;
rownames(multiExpr[[2]]$data) = names(M_Brain1)[-c(1:1)];
```


```{r}
# Check that the data has the correct format for many functions operating on multiple sets:
exprSize = checkSets(multiExpr)
```

```{r}
# Check that all genes and samples have sufficiently low numbers of missing values.
gsg = goodSamplesGenesMS(multiExpr, verbose = 3);
gsg$allOK
```

```{r}
if (!gsg$allOK)
{
# Print information about the removed genes:
if (sum(!gsg$goodGenes) > 0)
printFlush(paste("Removing genes:", paste(names(multiExpr[[1]]$data)[!gsg$goodGenes],
collapse = ", ")))
for (set in 1:exprSize$nSets)
{

if (sum(!gsg$goodSamples[[set]]))
printFlush(paste("In set", setLabels[set], "removing samples",
paste(rownames(multiExpr[[set]]$data)[!gsg$goodSamples[[set]]], collapse = ", ")))
# Remove the offending genes and samples
multiExpr[[set]]$data = multiExpr[[set]]$data[gsg$goodSamples[[set]], gsg$goodGenes];
}
# Update exprSize
exprSize = checkSets(multiExpr)
}
```


```{r}
sampleTrees = list()
for (set in 1:nSets)
{
sampleTrees[[set]] = hclust(dist(multiExpr[[set]]$data), method = "average")
}
```

```{r}
pdf(file = "/Users/kchau/Documents/WGCNA/ConsensusBrainComparisonPCBonly/SamplesClustering.pdf", width = 12, height = 12);
par(mfrow=c(2,1))
par(mar = c(0, 4, 2, 0))
for (set in 1:nSets)
plot(sampleTrees[[set]], main = paste("Sample clustering on all genes in", setLabels[set]),
xlab="", sub="", cex = 0.7);
dev.off()
```


```{r}
# Choose the "base" cut height for the female data set
baseHeight = 60
# Adjust the cut height for the male data set for the number of samples
cutHeights = c(60, 60*exprSize$nSamples[2]/exprSize$nSamples[1]);
#cutHeights = c(60, 100);
# Re-plot the dendrograms including the cut lines
pdf(file = "/Users/kchau/Documents/WGCNA/ConsensusBrainComparisonPCBonly/SamplesClusteringCutoff.pdf", width = 12, height = 12);
par(mfrow=c(2,1))
par(mar = c(0, 4, 2, 0))
for (set in 1:nSets)
{
plot(sampleTrees[[set]], main = paste("Sample clustering on all genes in", setLabels[set]),
xlab="", sub="", cex = 0.7);
abline(h=cutHeights[set], col = "red");
}
dev.off()
```

```{r}
#outlier removal
for (set in 1:nSets)
{
   #Find clusters cut by the line
   labels = cutreeStatic(sampleTrees[[set]], cutHeight = cutHeights[set], minSize = 10)
   #Keep the largest one (labeled by the number 1)
   keep = (labels==1)
   multiExpr[[set]]$data = multiExpr[[set]]$data[keep, ]
 }
 
 labels1 <- cutreeStatic(sampleTrees[[1]], cutHeight = 60)
 labels2 <- cutreeStatic(sampleTrees[[2]], cutHeight = 100, minSize = 10)
```

```{r}
collectGarbage();
# Check the size of the leftover data
exprSize = checkSets(multiExpr)
exprSize
```


```{r}
PCBtraitData = read_excel("/Users/kchau/Documents/PEBBLES/sampletraits/M_F_Brains copy_combinations_PCB_only.xls")
#FAtraitData = read_excel("/Users/kchau/Documents/PEBBLES/RNA-seq/RawData/FolicAcidM_F_Brainscopy_combinations.xls")
#traitData <- traitData[-c(97:999),]
PCBtraitData <- PCBtraitData[!grepl("PLAC", PCBtraitData$Name),]
dim(PCBtraitData)
names(PCBtraitData)
```

```{r}
#allTraits = traitData[, c(1, 5, 7, 8)]
PCBallTraits = PCBtraitData[, -c(2,3,4, 6)]
PCBallTraits = PCBallTraits[-c(59:96),] #remove samples that had Folic Acid added
#FAallTraits = FAtraitData[, -c(6)]
#allTraits = PCBtraitData[, -c(4)]
#allTraits = traitData
# See how big the traits are and what are the trait and sample names
dim(PCBallTraits)
names(PCBallTraits)
PCBallTraits$Name
```

```{r}
#allTraits$Folic_Acid <- as.integer(as.factor(allTraits$Folic_Acid))
#library(plyr)
#FAallTraits$Folic_Acid <- revalue(FAallTraits$Folic_Acid, c("YES"=1))
#FAallTraits$Folic_Acid <- revalue(FAallTraits$Folic_Acid, c("NO"=0))
#allTraits$Sex <- revalue(allTraits$Sex, c("F"=0))
#allTraits$Sex <- revalue(allTraits$Sex, c("M"=1))
```


```{r}
#remove female brain outlier: 36_01; there are no male brain outliers
#allTraits <- allTraits[!grepl("35_05_BRAIN", allTraits$Name), ]
#allTraits <- allTraits[!grepl("35_06_BRAIN", allTraits$Name), ]
#PCBallTraits <- PCBallTraits[!grepl("36_01_BRAIN", PCBallTraits$Name), ]
#FAallTraits <- FAallTraits[!grepl("36_01_BRAIN", FAallTraits$Name), ]
```

```{r}
PCBallTraits <- PCBallTraits[ , -c(2, 4)]
```



```{r}
#PCB
# Form a multi-set structure that will hold the sample traits.
PCBTraits = vector(mode="list", length = nSets);
for (set in 1:nSets)
{
PCBsetSamples = rownames(multiExpr[[set]]$data);
PCBtraitRows = match(PCBsetSamples, PCBallTraits$Name);
PCBTraits[[set]] = list(data = PCBallTraits[PCBtraitRows, -1]);
rownames(PCBTraits[[set]]$data) = as.data.frame(PCBallTraits)[PCBtraitRows, 1]
#rownames(PCBTraits[[set]]$data) = as.data.frame(PCBallTraits)[PCBtraitRows, 1];
}
collectGarbage();
# Define data set dimensions
PCBnGenes = exprSize$nGenes;
PCBnSamples = exprSize$nSamples;
```


```{r}
# Choose a set of soft-thresholding powers
powers = c(seq(4,10,by=1), seq(12,40, by=2));
# Initialize a list to hold the results of scale-free analysis
powerTables = vector(mode = "list", length = nSets);
# Call the network topology analysis function for each set in turn
for (set in 1:nSets)
powerTables[[set]] = list(data = pickSoftThreshold(multiExpr[[set]]$data, powerVector=powers,
verbose = 2)[[2]]);
collectGarbage();
# Plot the results:
colors = c("black", "red")
# Will plot these columns of the returned scale free analysis tables
plotCols = c(2,5,6,7)
colNames = c("Scale Free Topology Model Fit", "Mean connectivity", "Median connectivity",
"Max connectivity");
# Get the minima and maxima of the plotted points
ylim = matrix(NA, nrow = 2, ncol = 4);
for (set in 1:nSets)
{
for (col in 1:length(plotCols))

{
ylim[1, col] = min(ylim[1, col], powerTables[[set]]$data[, plotCols[col]], na.rm = TRUE);
ylim[2, col] = max(ylim[2, col], powerTables[[set]]$data[, plotCols[col]], na.rm = TRUE);
}
}
# Plot the quantities in the chosen columns vs. the soft thresholding power
sizeGrWindow(8, 6)
pdf(file = "/Users/kchau/Documents/WGCNA/ConsensusBrainComparisonPCBonly/scaleFreeAnalysis.pdf", wi = 8, he = 6)
par(mfcol = c(2,2));
par(mar = c(4.2, 4.2 , 2.2, 0.5))
cex1 = 0.7;
for (col in 1:length(plotCols)) for (set in 1:nSets)
{
if (set==1)
{
plot(powerTables[[set]]$data[,1], -sign(powerTables[[set]]$data[,3])*powerTables[[set]]$data[,2],
xlab="Soft Threshold (power)",ylab=colNames[col],type="n", ylim = ylim[, col],
main = colNames[col]);
addGrid();
}
if (col==1)
{
text(powerTables[[set]]$data[,1], -sign(powerTables[[set]]$data[,3])*powerTables[[set]]$data[,2],
labels=powers,cex=cex1,col=colors[set]);
} else
text(powerTables[[set]]$data[,1], powerTables[[set]]$data[,plotCols[col]],
labels=powers,cex=cex1,col=colors[set]);
if (col==1)
{
legend("bottomright", legend = setLabels, col = colors, pch = 20) ;
} else
legend("topright", legend = setLabels, col = colors, pch = 20) ;
}
dev.off();
```


#increase minModuleSize to minimize number of modules
```{r}
#change back to 50 min module size
bnet = blockwiseConsensusModules(
multiExpr, maxBlockSize = PCBnGenes, power = 22, minModuleSize = 50,
networkType = "signed",
TOMType = "signed",
deepSplit = 2,
pamRespectsDendro = FALSE,
mergeCutHeight = 0.25, numericLabels = TRUE,
minKMEtoStay = 0,
saveTOMs = TRUE, verbose = 5)
```



```{r}
PCBconsMEs = bnet$multiMEs;
PCBmoduleLabels = bnet$colors;
# Convert the numeric labels to color labels
PCBmoduleColors = labels2colors(PCBmoduleLabels)
PCBconsTree = bnet$dendrograms[[1]]
```


```{r}
sizeGrWindow(12,6)

pdf(file = "/Users/kchau/Documents/WGCNA/ConsensusBrainComparisonPCBonly/PCBBlockwiseGeneDendrosAndColors.pdf", wi = 12, he = 6);
# Use the layout function for more involved screen sectioning
layout(matrix(c(1:4), 2, 2), heights = c(0.8, 0.2), widths = c(1,1))
#layout.show(4);
nBlocks = length(bnet$dendrograms)
# Plot the dendrogram and the module colors underneath for each block
for (block in 1:nBlocks)
plotDendroAndColors(bnet$dendrograms[[block]], PCBmoduleColors[bnet$blockGenes[[block]]],
"Module colors",
main = paste("Consensus Brain Gene dendrogram and module colors in block", block),
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05,
setLayout = FALSE)
dev.off()
```



```{r}
#find number of modules
table(bnet$colors)
```

```{r}
library(dplyr)
PCBTraits[[set]]$data <- PCBTraits[[set]]$data %>% 
    dplyr::select(-Sex, -LitterCoded)
```

```{r}
# Set up variables to contain the module-trait correlations
PCBmoduleTraitCor = list();
PCBmoduleTraitPvalue = list();
# Calculate the correlations
for (set in 1:nSets)
{
PCBmoduleTraitCor[[set]] = cor(PCBconsMEs[[set]]$data, PCBTraits[[set]]$data, use = "p", method = 'spearman');
PCBmoduleTraitPvalue[[set]] = corPvalueFisher(PCBmoduleTraitCor[[set]], exprSize$nSamples[set])
}
```


```{r}
# Convert numerical lables to colors for labeling of modules in the plot
PCBMEColors = labels2colors(as.numeric(substring(names(PCBconsMEs[[1]]$data), 3)));
PCBMEColorNames = paste("ME", PCBMEColors, sep="");
# Open a suitably sized window (the user should change the window size if necessary)
sizeGrWindow(10,7)
pdf(file = "/Users/kchau/Documents/WGCNA/ConsensusBrainComparisonPCBonly/hublitterConsensusModuleTraitRelationships-PCBfemale.pdf", wi = 12, he = 9);
# Plot the module-trait relationship table for set number 1
set = 1
textMatrix = paste(signif(PCBmoduleTraitCor[[set]], 2), "\n(",
signif(PCBmoduleTraitPvalue[[set]], 1), ")", sep = "");
dim(textMatrix) = dim(PCBmoduleTraitCor[[set]])
par(mar = c(6, 8.8, 3, 2.2));
labeledHeatmap(Matrix = PCBmoduleTraitCor[[set]],
xLabels = names(PCBTraits[[set]]$data),
yLabels = PCBMEColorNames,
ySymbols = PCBMEColorNames,
colorLabels = FALSE,
colors = greenWhiteRed(50),
textMatrix = textMatrix,
setStdMargins = FALSE,
cex.text = 0.7,
zlim = c(-1,1),
main = paste("ConsensusModule PCB trait relationships in", setLabels[set]))
dev.off();
# Plot the module-trait relationship table for set number 2
set = 2
textMatrix = paste(signif(PCBmoduleTraitCor[[set]], 2), "\n(",
signif(PCBmoduleTraitPvalue[[set]], 1), ")", sep = "");
dim(textMatrix) = dim(PCBmoduleTraitCor[[set]])
sizeGrWindow(10,7)
pdf(file = "/Users/kchau/Documents/WGCNA/ConsensusBrainComparisonPCBonly/hublitterConsensusModuleTraitRelationships-PCBmale.pdf", wi = 12, he = 9);
par(mar = c(6, 8.8, 3, 2.2));
labeledHeatmap(Matrix = PCBmoduleTraitCor[[set]],
xLabels = names(PCBTraits[[set]]$data),
yLabels = PCBMEColorNames,
ySymbols = PCBMEColorNames,
colorLabels = FALSE,
colors = greenWhiteRed(50),
textMatrix = textMatrix,
setStdMargins = FALSE,
cex.text = 0.7,
zlim = c(-1,1),
main = paste("ConsensusModule PCB Trait Relationships in", setLabels[set]))
dev.off()
```


```{r}
# Initialize matrices to hold the consensus correlation and p-value
PCBconsensusCor = matrix(NA, nrow(PCBmoduleTraitCor[[1]]), ncol(PCBmoduleTraitCor[[1]]));
PCBconsensusPvalue = matrix(NA, nrow(PCBmoduleTraitCor[[1]]), ncol(PCBmoduleTraitCor[[1]]));
# Find consensus negative correlations
PCBnegative = PCBmoduleTraitCor[[1]] < 0 & PCBmoduleTraitCor[[2]] < 0;
PCBconsensusCor[PCBnegative] = pmax(PCBmoduleTraitCor[[1]][PCBnegative], PCBmoduleTraitCor[[2]][PCBnegative]);
PCBconsensusPvalue[PCBnegative] = pmax(PCBmoduleTraitPvalue[[1]][PCBnegative], PCBmoduleTraitPvalue[[2]][PCBnegative]);
# Find consensus positive correlations
PCBpositive = PCBmoduleTraitCor[[1]] > 0 & PCBmoduleTraitCor[[2]] > 0;
PCBconsensusCor[PCBpositive] = pmin(PCBmoduleTraitCor[[1]][PCBpositive], PCBmoduleTraitCor[[2]][PCBpositive]);
PCBconsensusPvalue[PCBpositive] = pmax(PCBmoduleTraitPvalue[[1]][PCBpositive], PCBmoduleTraitPvalue[[2]][PCBpositive])
```

```{r}
textMatrix = paste(signif(PCBconsensusCor, 2), "\n(",
signif(PCBconsensusPvalue, 1), ")", sep = "");
dim(textMatrix) = dim(PCBmoduleTraitCor[[set]])
sizeGrWindow(10,7)
pdf(file = "/Users/kchau/Documents/WGCNA/ConsensusBrainComparisonPCBonly/ModuleTraitRelationships-PCBconsensus.pdf", wi = 12, he = 9);
par(mar = c(6, 8.8, 3, 2.2));
labeledHeatmap(Matrix = PCBconsensusCor,
xLabels = names(PCBTraits[[set]]$data),
yLabels = PCBMEColorNames,
ySymbols = PCBMEColorNames,
colorLabels = FALSE,
colors = greenWhiteRed(50),
textMatrix = textMatrix,
setStdMargins = FALSE,
cex.text = 0.7,
zlim = c(-1,1),
main = paste("Consensus module PCB trait relationships across\n",
paste(setLabels, collapse = " and ")))
```



```{r}
# Create a variable weight that will hold just the body weight of mice in both sets
PCBDose = vector(mode = "list", length = nSets);
for (set in 1:nSets)
{
PCBDose[[set]] = list(data = as.data.frame(PCBTraits[[set]]$data$PCB_dose));
names(PCBDose[[set]]$data) = "PCB Dose"
}
# Recalculate consMEs to give them color names
consMEsC = multiSetMEs(multiExpr, universalColors = PCBmoduleColors);
# We add the weight trait to the eigengenes and order them by consesus hierarchical clustering:
MET = consensusOrderMEs(addTraitToMEs(consMEsC, PCBDose))
```

```{r}
sizeGrWindow(8,10);
pdf(file = "/Users/kchau/Documents/WGCNA/ConsensusBrainComparisonPCBonly/PCBEigengeneNetworks.pdf", width= 10, height = 12);
par(cex = 0.9)
plotEigengeneNetworks(MET, setLabels, marDendro = c(0,2,2,1), marHeatmap = c(3,3,2,1),
zlimPreservation = c(0.5, 1), xLabelsAngle = 90)
dev.off()
```


#HUB GENE

```{r}
hub <- chooseTopHubInEachModule(
   datExpr, 
   bnet$colors, 
   omitColors = "grey", 
   power = 2, 
   type = "signed")
```

```{r}
moduleLookup <- data.frame(
  ModuleNumber = sort(unique(bnet$colors)),
  ModuleColor  = labels2colors(sort(unique(bnet$colors)))
)

moduleLookup
```

```{r}
hub_df <- data.frame(
  ModuleNumber = as.numeric(names(hub)),
  HubGene      = unname(hub)
)

hub_df <- merge(hub_df, moduleLookup, by = "ModuleNumber")
```

```{r}
?chooseOneHubInEachModule
```


```{r}
Onehubgene <- chooseOneHubInEachModule(
   datExpr, 
   bnet$colors,  
   numGenes = 100, 
   omitColors = "grey", 
   power = 2, 
   type = "signed")

```

```{r}
onehubmoduleLookup <- data.frame(
  ModuleNumber = sort(unique(bnet$colors)),
  ModuleColor  = labels2colors(sort(unique(bnet$colors)))
)

onehubmoduleLookup
```

```{r}
onehub_df <- data.frame(
  ModuleNumber = as.numeric(names(Onehubgene)),
  HubGene      = unname(Onehubgene)
)

onehub_df <- merge(onehub_df, onehubmoduleLookup, by = "ModuleNumber")
```



```{r}
library(biomaRt)

ensembl <- useEnsembl(
  biomart = "genes",
  dataset = "mmusculus_gene_ensembl",
  mirror  = "useast"
)

annot <- getBM(
  attributes = c("ensembl_gene_id", "mgi_symbol"),
  filters    = "ensembl_gene_id",
  values     = hub_df$HubGene,
  mart       = ensembl
)

hub_df <- merge(
  hub_df,
  annot,
  by.x = "HubGene",
  by.y = "ensembl_gene_id",
  all.x = TRUE
)

```

```{r}

ensembl <- useEnsembl(
  biomart = "genes",
  dataset = "mmusculus_gene_ensembl",
  mirror  = "useast"
)

annot <- getBM(
  attributes = c("ensembl_gene_id", "mgi_symbol"),
  filters    = "ensembl_gene_id",
  values     = onehub_df$HubGene,
  mart       = ensembl
)

onehub_df <- merge(
  onehub_df,
  annot,
  by.x = "HubGene",
  by.y = "ensembl_gene_id",
  all.x = TRUE
)

```

```{r}
hub_kME <- sapply(colnames(MEs), function(ME) {
  module <- sub("^ME", "", ME)          # e.g. "blue"
  genesInModule <- moduleColors == module
  
  rownames(kME)[genesInModule][
    which.max(abs(kME[genesInModule, ME]))
  ]
})
```

```{r}
MET <- consensusModuleEigengenes(
  multiExpr,
  colors = moduleColors,
  excludeGrey = TRUE
)$eigengenes
```

```{r}
consensusColors <- bnet$colors
moduleColors <- consensusColors
moduleColors <- labels2colors(moduleColors)

nSets <- length(multiExpr)

colorsMat <- matrix(
  moduleColors,
  nrow = length(moduleColors),
  ncol = nSets
)

colnames(colorsMat) <- paste0("set", 1:nSets)

colorsList <- list(
  moduleColors,
  moduleColors
)


MET <- multiSetMEs(
  multiExpr,
  colors = moduleColors,
  excludeGrey = TRUE
)
```


```{r}
datExpr <- multiExpr[[1]]$data
kMEtable <- signedKME(multiExpr, MET)

```


```{r}
kME1 <- kME[[1]]$cor
kME2 <- kME[[2]]$cor

moduleLabels <- as.numeric(factor(moduleColors))


hubGenes <- sapply(colnames(kME1), function(ME) {

  moduleLabel <- as.numeric(sub("^ME", "", ME))  # 1, 2, ...

  genesInModule <- moduleLabels == moduleLabel
  geneNames <- rownames(kME1)[genesInModule]

  meanKME <- (abs(kME1[genesInModule, ME]) +
              abs(kME2[genesInModule, ME])) / 2

  geneNames[which.max(meanKME)]
})

hubGenes
```





```{r}
library("AnnotationDbi")
library("org.Mm.eg.db")
#columns(org.Mm.eg.db) # returns list of available keytypes
F_Brain1$entrez = mapIds(org.Mm.eg.db,
                    keys=F_Brain1$Gene, #Column containing Ensembl gene ids
                    column="ENTREZID",
                    keytype="ENSEMBL",
                    multiVals="first")
```



```{r}
#columns(org.Mm.eg.db) # returns list of available keytypes
M_Brain1$entrez = mapIds(org.Mm.eg.db,
                    keys=M_Brain1$Gene, #Column containing Ensembl gene ids
                    column="ENTREZID",
                    keytype="ENSEMBL",
                    multiVals="first")
```


```{r}
#GO Terms Female Brain
GOenrFemaleBrain = GOenrichmentAnalysis(PCBmoduleColors, F_Brain1$entrez, organism = "mouse", evidence = "all", nBestP = 10)

#GO Terms Male Brain
GOenrMaleBrain = GOenrichmentAnalysis(PCBmoduleColors, M_Brain1$entrez, organism = "mouse", evidence = "all", nBestP = 10)
```



```{r}
tabFemaleBrain = GOenrFemaleBrain$bestPTerms[[4]]$enrichment
tabMaleBrain = GOenrMaleBrain$bestPTerms[[4]]$enrichment
```

```{r}
write.table(tabFemaleBrain, file = "/Users/kchau/Documents/WGCNA/ConsensusBrainComparisonPCBonly/ConsensusFemaleBrainGOEnrichmentTable.csv", sep = ",", quote = TRUE, row.names = FALSE)

write.table(tabMaleBrain, file = "/Users/kchau/Documents/WGCNA/ConsensusBrainComparisonPCBonly/ConsensusMaleBrainGOEnrichmentTable.csv", sep = ",", quote = TRUE, row.names = FALSE)
```





#For Consensus GO terms
```{r}
consMEs.unord = multiSetMEs(multiExpr, universalColors = PCBmoduleLabels, excludeGrey = TRUE)
GS = list();
kME = list();
for (set in 1:nSets)
{
GS[[set]] = corAndPvalue(multiExpr[[set]]$data, PCBTraits[[set]]$data);
kME[[set]] = corAndPvalue(multiExpr[[set]]$data, consMEs.unord[[set]]$data);
}
```

```{r}
GS.metaZ = (GS[[1]]$Z + GS[[2]]$Z)/sqrt(2);
kME.metaZ = (kME[[1]]$Z + kME[[2]]$Z)/sqrt(2);
GS.metaP = 2*pnorm(abs(GS.metaZ), lower.tail = FALSE);
kME.metaP = 2*pnorm(abs(kME.metaZ), lower.tail = FALSE)
```

```{r}
GSmat = rbind(GS[[1]]$cor, GS[[2]]$cor, GS[[1]]$p, GS[[2]]$p, GS.metaZ, GS.metaP);
nTraits = checkSets(PCBTraits)$nGenes
traitNames = colnames(PCBTraits[[1]]$data)
dim(GSmat) = c(PCBnGenes, 6*nTraits)
#rownames(GSmat) = probes;
rownames(GSmat) = M_Brain1$Gene;
colnames(GSmat) = spaste(
c("GS.set1.", "GS.set2.", "p.GS.set1.", "p.GS.set2.", "Z.GS.meta.", "p.GS.meta"),
rep(traitNames, rep(6, nTraits)))
# Same code for kME:
kMEmat = rbind(kME[[1]]$cor, kME[[2]]$cor, kME[[1]]$p, kME[[2]]$p, kME.metaZ, kME.metaP);
MEnames = colnames(consMEs.unord[[1]]$data);
nMEs = checkSets(consMEs.unord)$nGenes
dim(kMEmat) = c(PCBnGenes, 6*nMEs)
#rownames(kMEmat) = probes;
rownames(kMEmat) = M_Brain1$Gene;
colnames(kMEmat) = spaste(
c("kME.set1.", "kME.set2.", "p.kME.set1.", "p.kME.set2.", "Z.kME.meta.", "p.kME.meta"),
rep(MEnames, rep(6, nMEs)))
```

```{r}
info = data.frame(Probe = M_Brain1$Gene, EntrezID = M_Brain1$entrez,
ModuleLabel = PCBmoduleLabels,
ModuleColor = labels2colors(PCBmoduleLabels), GSmat, kMEmat);
write.csv(info, file = "/Users/kchau/Documents/WGCNA/ConsensusBrainComparisonPCBonly/testingbrain_consensusAnalysis-CombinedNetworkResults.csv",
row.names = FALSE, quote = FALSE)
```

```{r}
info <- read.csv("/Users/kchau/Documents/WGCNA/ConsensusBrainComparisonPCBonly/testingbrain_consensusAnalysis-CombinedNetworkResults.csv")
```


```{r}
hubTable <- do.call(rbind, lapply(sort(unique(info$ModuleLabel)), function(m) {

  colname <- paste0("Z.kME.meta.ME", m)

  # skip modules without eigengenes (e.g. grey)
  if (!colname %in% colnames(info)) return(NULL)

  sub <- info[info$ModuleLabel == m, ]

  # force numeric (guards against factor/character conversion)
  zvals <- as.numeric(sub[[colname]])

  sub[which.max(abs(zvals)), ]
}))

```


```{r}
nrow(hubTable)
length(unique(hubTable$ModuleLabel))
any(hubTable$ModuleColor == "grey")
```




```{r}
# kME1 is the correlation matrix: genes × MEs
ME2color <- sapply(colnames(kME1), function(ME) {

  # genes whose strongest membership is this ME
  genesInModule <- apply(abs(kME1), 1, function(x)
    colnames(kME1)[which.max(x)] == ME
  )

  # most common color among those genes
  names(sort(table(moduleColors[genesInModule]), decreasing = TRUE))[1]
})

ME2color
```



```{r}
info <- info[, c(1:4)]
info$GeneSymbol <- 'NA'

#Convert entrezID to gene symbols using biomart
library(biomaRt)
library(dplyr)
library(xlsx)


mart <- useDataset("mmusculus_gene_ensembl", useMart("ensembl"))
#got the probe and gene symbol that matches
geneSymbols <- getBM(filters = "ensembl_gene_id", attributes= c("ensembl_gene_id", "external_gene_name"), values=info$Probe, mart= mart)

#join the dataframe with moduleinfo by Probe column
joinGeneSymbol <- left_join(info, geneSymbols, by = c("Probe" = "ensembl_gene_id"))
```


```{r}
#split function
modulecolors_split <- split(joinGeneSymbol, joinGeneSymbol$ModuleColor)


# Assuming you have a list of module colors and their corresponding data frames
#module_colors <- c('red', 'blue', 'green', ...)  # Add other module colors as needed
#module_data_frames <- list(red = redmodule, blue = bluemodule, green = greenmodule, ...)  # Replace with actual data frames for other modules

# Create a function to perform enrichment analysis and save the results
perform_enrichment <- function(module_color, module_data) {
  enriched_data <- enrichR::enrichr(
    module_data$external_gene_name,
    c('GO_Biological_Process_2023', 'GO_Cellular_Component_2023', 'GO_Molecular_Function_2023')
  )
  file_path <- sprintf("/Users/kchau/Documents/WGCNA/ConsensusBrainComparisonPCBonly/GO_terms/%s_excel.xlsx", module_color)
  openxlsx::write.xlsx(enriched_data, file_path)
}

# Loop through each module color and perform enrichment analysis
for (color in names(modulecolors_split)) {
  module_data <- modulecolors_split[[color]]
  perform_enrichment(color, module_data)
}
```


```{r}
# Choose interesting modules
intModules = c("MEbrown")
for (module in intModules)
{
#Select module probes
modGenes = (moduleColors==module)
#Get their entrez ID codes
modLLIDs = F_Brain1$entrez[modGenes];
#Write them into a file
fileName = paste("LocusLinkIDs-", module, ".txt", sep="");
write.table(as.data.frame(modLLIDs), file = "/Users/kchau/Documents/WGCNA/ConsensusBrainComparison/outputgenelist",
row.names = FALSE, col.names = FALSE)
}
```

```{r}
install.packages("onewaytests")
library(onewaytests)
bf.test()
```

```{r}
MEtrait <- PCBtraitData[c(1:6)]

femaleMEtrait <- MEtrait %>% filter(PCBtraitData$Sex == "F")
femaleMEtrait <- femaleMEtrait[-c(32:51),] #remove samples with Folate

femaleME_lightcyan_traits <- cbind(femaleMEtrait, MET[[1]]$data$MElightcyan)

femaleME_lightcyan_traits$PCB_dose <- as.factor(femaleME_lightcyan_traits$PCB_dose)


ggplotPCBEffect_lightcyan <- ggplot(data = femaleME_lightcyan_traits, aes(x = PCB_dose, y = MET[[1]]$data$MElightcyan, color = PCB_dose)) + geom_boxplot() + geom_point() + ggtitle("PCB Dosage Effect in Female Brain: Eigengene Values in Light Cyan Module") + xlab("PCB Dose (mg/kg/day)") + ylab("Module Eigengene Value")
                                     
ggplotPCBEffect_lightcyan + theme(text = element_text(size = 10)) + geom_point(size=2) + ylim(-0.4, 0.4)
```

```{r}
MEtrait <- PCBtraitData[c(1:6)]

maleMEtrait <- MEtrait %>% filter(PCBtraitData$Sex == "M")
maleMEtrait <- maleMEtrait[-c(28:45),] #remove samples with Folate

maleME_lightcyan_traits <- cbind(maleMEtrait, MET[[2]]$data$MElightcyan)

maleME_lightcyan_traits$PCB_dose <- as.factor(maleME_lightcyan_traits$PCB_dose)


ggplotPCBEffect_lightcyan_male <- ggplot(data = maleME_lightcyan_traits, aes(x = PCB_dose, y = MET[[2]]$data$MElightcyan, color = PCB_dose)) + geom_boxplot() + geom_point() + ggtitle("PCB Dosage Effect in Male Brain: Eigengene Values in Light Cyan Module") + xlab("PCB Dose (mg/kg/day)") + ylab("Module Eigengene Value")
                                     
ggplotPCBEffect_lightcyan_male + theme(text = element_text(size = 10)) + geom_point(size=2) + ylim(-0.4, 0.4)
```









```{r}
ggplotTurquoise_male_new <- ggplot(data = MEturquoise_male, aes(x = FA_PCB, y = MET[[2]]$data$MEturquoise, color = FA_PCB)) + geom_boxplot() + geom_point() + ggtitle("Male Brain: Eigengene Values in Turquoise Module") + xlab("Treatment") + ylab("Module Eigengene Values")
```




```







```{r}
#make the female Module Eigengene Dataframe
MEtrait <- traitData[c(1:4)]


MEtrait <- MEtrait[c(1:6, 14:23, 29:37, 44:49, 59:68, 77:86), ] #filter out the males
MEtrait <- subset(MEtrait, MEtrait$Name != '36_01_BRAIN') #remove the outlier in female samples
```

```{r}
MEturquoiseandtraits <- cbind(MEtrait, MET[[1]]$data$MEturquoise)
```

```{r}
summary(MEturquoiseandtraits$`MET[[1]]$data$MEturquoise`)
```

```{r}
MEturquoiseandtraits$highorlowdose <- c(1:50)
MEturquoiseandtraits$highorlowdose[1:16] <- "low_dose"
MEturquoiseandtraits$highorlowdose[17:31] <- "high_dose"
MEturquoiseandtraits$highorlowdose[32:50] <- "low_dose"
```



#want a boxplot separated by Yes Folic Acid (2 bars referring to 0 and 0.1 PCB) and No Folic Acid (2 bars reffering to 0 and 0.1 PCB dose)


```{r}
MEturquoiseandtraits$FA_PCB <- paste(MEturquoiseandtraits$Folic_Acid, MEturquoiseandtraits$PCB_dose, sep = "-")
```

```{r}
MEturquoiseandtraits$FA_PCB <- as.factor(MEturquoiseandtraits$FA_PCB)
#levels(MEturquoiseandtraits$FA_PCB) <- c("No FA, No PCB", "No FA, Yes PCB", "Yes FA, No PBC", "Yes FA, Yes PCB")
```


```{r}
ggplotTurquoise_female_new <- ggplot(data = MEturquoiseandtraits, aes(x = FA_PCB, y = MET[[1]]$data$MEturquoise, color = FA_PCB)) + geom_boxplot() + geom_point() + ggtitle("Female Brain: Eigengene Values in Turquoise Module") + xlab("Treatment") + ylab("Module Eigengene Values")
```

```{r}
ggplotTurquoise_female_new
```

1) red and blue paired together, yellow and pink together (Folate Effect)
subset


```{r}
MEturquoise_female_folateeffect <- MEturquoiseandtraits[c(1:16, 32:50), ]

MEturquoise_female_folateeffect$FA_PCB <- factor(MEturquoise_female_folateeffect$FA_PCB, levels=c("NO-0", "YES-0", "NO-0.1", "YES-0.1"))

ggplotTurquoise_female_folateeffect <- ggplot(data = MEturquoise_female_folateeffect, aes(x = FA_PCB, y = MEturquoise_female_folateeffect$`MET[[1]]$data$MEturquoise`, color = FA_PCB)) + geom_boxplot() + geom_point() + ggtitle("Folate Effect in Female Brain: Eigengene Values in Turquoise Module") + xlab("Folic Acid - PCB Dose") + ylab("Module Eigengene Value")

ggplotTurquoise_female_folateeffect




```






2) without folate (PCB dosage effect) #add color


```{r}
MEfolateeffect <- MEturquoiseandtraits
MEfolateeffect <- MEturquoiseandtraits[1:31, ] #only include samples with no folate
MEfolateeffect$PCB_dose <- as.character(MEfolateeffect$PCB_dose)

ggplotFolateEffect <- ggplot(data = MEfolateeffect, aes(x = MEfolateeffect$FA, y = MEfolateeffect$`MET[[1]]$data$MEturquoise`, color = MEfolateeffect$PCB_dose)) + geom_boxplot() + geom_point() + ggtitle("PCB Dosage Effect in Female Brain: Eigengene Values in Turquoise Module") + xlab("PCB Dose (mg/kg/day)") + ylab("Module Eigengene Value")


ggplotFolateEffect + theme(legend.position = "none")
```


#Plot Male 

```{r}
MEtrait_male <- traitData[c(1:4)]
MEtrait_male <- MEtrait_male[c(7:13, 24:28, 38:43, 50:58, 69:76, 87:96), ] #filter out the females
#filter out male outliers
MEtrait_male <- subset(MEtrait_male, MEtrait_male$Name != '35_05_BRAIN') #remove the outlier in male samples
MEtrait_male <- subset(MEtrait_male, MEtrait_male$Name != '35_06_BRAIN') #remove the outlier in male samples
```


```{r}
MEturquoise_male <- cbind(MEtrait_male, MET[[2]]$data$MEturquoise)
```


```{r}
MEturquoise_male$FA_PCB <- paste(MEturquoise_male$Folic_Acid, MEturquoise_male$PCB_dose, sep = "-")
```

```{r}
MEturquoise_male$FA_PCB <- as.factor(MEturquoise_male$FA_PCB)
#levels(MEturquoiseandtraits$FA_PCB) <- c("No FA, No PCB", "No FA, Yes PCB", "Yes FA, No PBC", "Yes FA, Yes PCB")
```


```{r}
ggplotTurquoise_male_new <- ggplot(data = MEturquoise_male, aes(x = FA_PCB, y = MET[[2]]$data$MEturquoise, color = FA_PCB)) + geom_boxplot() + geom_point() + ggtitle("Male Brain: Eigengene Values in Turquoise Module") + xlab("Treatment") + ylab("Module Eigengene Values")
```

```{r}
ggplotTurquoise_male_new
```
```{r}
MEturquoise_male_folateeffect <- MEturquoise_male[c(1:12, 28:43), ]


MEturquoise_male_folateeffect$FA_PCB <- factor(MEturquoise_male_folateeffect$FA_PCB, levels=c("NO-0", "YES-0", "NO-0.1", "YES-0.1"))

ggplotTurquoise_male_folateeffect <- ggplot(data = MEturquoise_male_folateeffect, aes(x = FA_PCB, y = MEturquoise_male_folateeffect$`MET[[2]]$data$MEturquoise`, color = FA_PCB)) + geom_boxplot() + geom_point() + ggtitle("Folate Effect in Male Brain: Eigengene Values in Turquoise Module") + xlab("Folate - PCB Dose (mg/kg/day)") + ylab("Module Eigengene Value")

ggplotTurquoise_male_folateeffect


```









1) red and blue paired together, yellow and pink together (Folate Effect)

2) without folate (PCB dosage effect) #add color

```{r}


MEfolateeffect_male <- MEturquoise_male
MEfolateeffect_male <- MEturquoise_male[1:27, ] #only include samples with no folate
MEfolateeffect_male$FA_PCB <- MEfolateeffect_male$PCB_dose

MEfolateeffect_male$PCB_dose <- as.character(MEfolateeffect_male$PCB_dose)

ggplotFolateEffect_male <- ggplot(data = MEfolateeffect_male, aes(x = MEfolateeffect_male$PCB_dose, y = MEfolateeffect_male$`MET[[2]]$data$MEturquoise`, color = MEfolateeffect_male$PCB_dose)) + geom_boxplot() + geom_point()  + ggtitle("PCB Dosage Effect in Male Brain: Eigengene Values in Turquoise Module") + xlab("PCB Dose (mg/kg/day)") + ylab("Module Eigengene Value")


ggplotFolateEffect_male + theme(legend.position = "none")
```

